Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex

[Results Here]

\section{Future Work}

>>>>

Upon the completion of {\em Kimbee}, we met with Mr. Kreider in order to assess how a professional speech therapist would respond to the application and to see if he had any suggestions and improvements \cite{Kreider:Results}. His reaction was very positive. He found no real flaws with the application and expressed that it would be very useful for children and his work with the children he works with. He did have suggestions for the future that are listed below under section \ref{sec:future_work}. Unfortunately we did not have time to test our application with actual children and track the results but we are confident that {\em Kimbee} can be used in a real world setting.

\section{Future Work}
\label{sec:future_work}
